An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-28 draft.tex
Some corrections here and there

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{pool_island}
    \caption{Population State and dataflow between processing nodes of a Pool-based multi-population algorithm.}
    \label{fig:pool_island}
\end{figure}

@@

Having a multi-population based algorithm can decrease the execution time
because of the parallel execution of the evolution. But, having heterogeneous 
populations might enhance evolutionary search and needless
evaluations than homogeneous systems; heterogeneous settings, if
done right, increases the diversity of the whole population \cite{araujo2008multikulti}. % cita
                                % multikulti o similar - JJ

% Explain that heterogeneity comes from using different algorithms,
% not from using different types of nodes - JJ 
% done - Mario 
But this is a rule of thumb, and it will depend on the degree of heterogeneity,
as well as on the algorithm itself. Some level of heterogeneity can be
implemented by just changing the configuration parameters of each population,
but in this case, we are interested in a heterogeneous search strategy. 
Therefore, in this experiment we compare a multi-population with only GA and PSO populations,
versus an ensemble of GA and PSO algorithms. We tested on the first five functions of the
BOBB testbed. We used ten populations and 8 workers for the experiment and the
same parameters as before.

\subsection{Hardware}
\label{sec:hardware}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{ Time required to complete experiments with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{pool_island}
    \caption{Population state and flow of data between processing nodes of a Pool-based multi-population algorithm.}
    \label{fig:pool_island}
\end{figure}

@@

Having a multi-population based algorithm can decrease the execution time
because of the parallel execution of the evolution. But, having heterogeneous 
populations might enhance evolutionary search and needless
evaluations than homogeneous systems; heterogeneous settings, if
done right, increases the diversity of the whole population
\cite{araujo2008multikulti}.

But this is a rule of thumb, and it will depend on the degree of heterogeneity,
as well as on the algorithm itself. Some level of heterogeneity can be
implemented by just changing the configuration parameters of each population,
but in this case, we are interested in a heterogeneous search strategy. 
Therefore, in this experiment we compare a multi-population with only GA and PSO populations,
versus an ensemble of GA and PSO algorithms. We tested on the first five functions of the
BOBB testbed. We used ten populations and eight workers for the experiment and the
same parameters as before.

% Shouldn't this be a subsection of experimental setup? - JJ
\subsection{Hardware}
\label{sec:hardware}

@@

\begin{figure}[h!tb]
  % Is the axis correct? Seconds per instance or total time? Please
  % change that - JJ
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{Time required to complete experiments with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}
